%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Achievements}
\noindent

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


%---------------------------------------------------------
  \begin{cventries}

%---------------------------------------------------------
\begin{cvitems} % Description(s) bullet points
\item{ {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Awarded with \textbf{Certificate of Excellence Top Ranker 2019 }for performance at university examination of 3\textsuperscript{rd} year.}}
\item{{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Received \textbf{Placement offer from TCS} for the Digital role through CodeVita 2019,  \textbf{Infosys} for System Engineer Specialist role through HackWithInfy 2019 and from \textbf{Crest Data systems} for a Developer role.}}
% \item{Received \textbf{Placement offer from Infosys} for System Engineer Specialist role through hackwithinfy 2019.}
% \item{Received \textbf{Placement offer from Crest Data systems} for Developer role.}
\item{{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}Highest CodeChef rating \textbf{1856(4-star)}}.}
\item{{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} One of my projects 'My Instant Notes' has obtained \textbf{500+ national and international} downloads and \textbf{4.9/5 ratings on Google PlayStore} with \textbf{zero crash report} to date.}}
 \item {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Secured \textbf{700/800 marks }in National Programming Aptitude Test (NPAT).\href{https://drive.google.com/open?id=19GsoeP4D9Bw4d8MdDmASp_mzMwAXBJOp}{ Link}.}
 \item {{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Achieved\textbf{ Global Rank 1} in the qualification round of Snackdown19, an annual global programming tournament conducted by CodeChef and obtained global rank 436 in the next round.\href{https://www.codechef.com/certificates/public/769487e}{ Link.}}}
 \item {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Achieved \textbf{Global Rank 138} in CodeChef Long Challenge June’19B }
 \item {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} {Secured Internship with a stipend from Internshala in Fifth Semester (2018) by clearing several rounds of the selection process. I stood in the \textbf{top five among 200+ participants} for the internship at Fireblaze Pvt. Ltd.}}
 \item{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Qualified for TCS CodeVita round 2 by securing a position in the \textbf{top 1000 (for CodeVita 2018)} and \textbf{top 550 (for CodeVita 2019)}. Also cleared qualification round of Google CodeJam 2019.}
  \item {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} {Achieved \textbf{98\%} in Machine Learning and Neural Networks and Deep Learning courses offered by Stanford University and deeplearning.ai respectively on Coursera }}
\item {\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text} Secured ELITE Grade in various courses like Programming, Data Structures and Algorithms using Python- 2017 (\href{https://nptel.ac.in/noc/Ecertificate/?q=noc17-cs28/NPTEL17CS28S1140194171011045.jpg}{Link}), Programming in C++ -2017 (\href{https://nptel.ac.in/noc/Ecertificate/?q=noc17-cs24/NPTEL17CS24S2150185171011045.jpg}{Link}) and Introduction to Modern Application Development - 2018 (\href{https://nptel.ac.in/noc/Ecertificate/?q=noc18-cs03/NPTEL18CS03S31601201810063149.jpg}{Link}) offered by IITs and IISc under National Programme for Technology Enhanced Learning (NPTEL).}
       
\end{cvitems}
   \vspace{0.5 cm}   
\end{cventries}
